A quantum parallel Markov chain Monte Carlo

### 2022-07-29 main.tex
just need discussion and general cleaning

In the following section, we provide a \emph{very} short introduction to the most basic elements of quantum computing. The interested reader may look to \citet{nielsen2002quantum} for a canonical introduction to quantum algorithms and their implementation.

@@

\begin{prop}[Warm-starting]\label{prop:warm}
	Suppose that the quantum minimization algorithm begins with a threshold $F_0$ such that $f(x)<F_0$ for only $K-1$ items. Then the expected total number of time steps to find the minimizer is bounded above by
	\begin{align*}
	m_0^K = \left(\frac{5}{4} - \frac{1}{\sqrt{K-1}} \right) 9\sqrt{N} + \frac{7}{10} \log_2(K) \log_2(N) \, ,
	\end{align*}
	and so the following rule relates the warm-started upper bound to the generic upper bound:
	\begin{align*}
	m_0^K = m_0 - 9\sqrt{\frac{N}{K-1}} + \frac{7}{10} \log_2 \left(\frac{K}{N} \right) \log_2(N)\, .
	\end{align*} 
\end{prop}

@@

\section{Quantum parallel MCMC}

@@

 \begin{figure}[!t]
 	\vspace{3em}
	\centering
	\includegraphics[width=0.9\linewidth]{mcmcIterations.pdf}
	\caption{Total number of oracle evaluations required for each of 2,000 parallel MCMC iterations. In total, the combined MCMC runs required roughly $7$\% of the usual 20 million target evaluations. Over  99.4\% of the 10,000 MCMC iterations successfully sampled from the discrete distribution with probabilities of Equation \eqref{eq:probs}. Burn-in evaluations require moderately more evaluations because the current state occupies a lower density region and represents a `less good' warm-start.}\label{fig:mcmcIterations}
\end{figure}

>>>>

We provide a short introduction to the most basic elements of quantum computing in Appendix \ref{sec:shortIntro}. The interested reader may look to \citet{nielsen2002quantum} for a canonical introduction to quantum algorithms or \citet{lopatnikova2021introduction,wang2022quantum} for surveys geared toward statisticians.   In Section \ref{sec:qSearch}, we review and compare three different quantum search algorithms that enjoy quadratic speedups over conventional algorithms.  In Section \ref{sec:qmin} we review the quantum minimization algorithm of \citet{durr1996quantum} and investigate the use of warm-starting therein.  We then review the Gumbel-max trick (Section \ref{sec:gm}) and recent insights in parallel MCMC (Section \ref{sec:sym}) before combining these ideas with quantum minimization to create the quantum parallel MCMC algorithm.

@@

\begin{prop}[Warm-starting]\label{prop:warm}
	Suppose that the quantum minimization algorithm begins with a threshold $F_0$ such that $f(x)<F_0$ for only $K-1>0$ items. Then the expected total number of time steps to find the minimizer is bounded above by
	\begin{align*}
	m_0^K = \left(\frac{5}{4} - \frac{1}{\sqrt{K-1}} \right) 9\sqrt{N} + \frac{7}{10} \log_2(K) \log_2(N) \, ,
	\end{align*}
	and so the following rule relates the warm-started upper bound to the generic upper bound:
	\begin{align*}
	m_0^K = m_0 - 9\sqrt{\frac{N}{K-1}} + \frac{7}{10} \log_2 \left(\frac{K}{N} \right) \log_2(N)\, .
	\end{align*} 
\end{prop}

@@

\section{Quantum parallel MCMC}\label{sec:qpmcmc}

@@

 \begin{figure}[!t]
 	\vspace{3em}
	\centering
	\includegraphics[width=0.9\linewidth]{mcmcIterations.pdf}
	\caption{Total number of oracle evaluations required for each of 2,000 parallel MCMC iterations. In total, the combined MCMC runs required roughly $7$\% of the usual 20 million target evaluations. Over  99.4\% of the 10,000 MCMC iterations successfully sampled from the discrete distribution with probabilities of Equation \eqref{eq:probs}. Burn-in iterations require moderately more evaluations because the current state occupies a lower density region and represents a `less good' warm-start.}\label{fig:mcmcIterations}
\end{figure}
